\begin{sol}
\begin{enumerate}
\item[\textbf{(1)}]
\begin{equation}
	\{M^i,M^j\}=2\delta^{ij}\mathbf{1}\implies M^iM^i=\mathbf{1}
\end{equation}  
Firstly, the eigenvalue of $(M^i)^2$ must be 1 since it is identical to the identity, which by definition, has all vectors as eigenvectors with eigenvalue 1. 
Let $\ket\phi$ be an eigenvector of $M^i$ with eigenvalue $\lambda$, then, $(M^i)^2\ket\phi=\lambda^2\ket\phi$. Since it has been shown that the eigenvalues of $(M^i)^2$ must be $1$, $\lambda^2=1$ thus $\lambda=\pm 1$.
\item[\textbf{(2)}]
\begin{equation}
	\{M^i,M^j\}=2\delta^{ij}\mathbf{1}\implies M^iM^j=-M^jM^i\text{ for }i\neq j
\end{equation}
As it is known that $M^iM^i=\mathbf{1}$, thus, $M^i$ must be invertible.
\begin{equation}
	M^i=-M^jM^i(M^j)^{-1}\text{ for }i\neq j
\end{equation}
\begin{equation}
	\Tr(M^i)=M^i_{nn}=-(M^jM^i(M^j)^{-1})_{nn}=-(M^j_{nl}M^i_{lm}(M^j)^{-1}_{mn})
\end{equation}
\begin{equation}
	=-((M^j)^{-1}_{mn}M^j_{nl}M^i_{lm})=-\mathbf 1_{ml}M^i_{lm}=-M^i_{ll}=-\Tr(M^i)
\end{equation}
It is shown that $\Tr(M^i)=-\Tr(M^i)$, thus, $M^i$ must be traceless.\\\\Note that the choice of $M^j$ is irrelevant to the problem and for any invertible matrix $S$, $\Tr(M)=\Tr(SMS^{-1})$. This fact will be used later.
\item[\textbf{(3)}]
It is shown that all matrices that satisfy the relation $\{M^i,M^j\}=2\delta^{ij}\mathbf{1}$ must be traceless and be its own inverse.\\
Assume there exists a set of four matrices that are odd dimensional which satisfies these relations. All matrices can be factored in the form of $M^i=S^iJ^i(S^i)^{-1}$, where $J^i$ is the matrix for $M^i$ written in Jordon canonical form. In this form, the diagonals are the eigenvalues of the matrix. Thus, $\Tr(M^i)=\Tr(S^iJ^i(S^i)^{-1})=\Tr(J^i)=0$. This is a sum of eigenvalues. However, it has also been shown that all eigenvalues of $M^i$ must be either $-1$ and $1$, which are both odd numbers. It is also well known that a sum of a odd amount of odd numbers is a odd number. Thus, for a odd-dimensional matrix the trace must be an odd number. However, zero is not an odd number, which is a contradiction. Therefore, there are no odd set of odd-dimensional matrices that satisfy $\{M^i,M^j\}=2\delta^{ij}\mathbf{1}$.
\end{enumerate}
\end{sol}